The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth

### 2021-09-16 paper/paper-jsdse/paper-jsdse.Rmd
author fixed

---
title: "The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth"
authors:
  - name: Dewi Amaliah
    thanks: ""
    department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    location: Clayton, VIC 3800
    email: dama0007@student.monash.edu
  - name: Dianne Cook
    department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    location: Clayton, VIC 3800
    email: dicook@monash.edu
  - name: Emi Tanaka
    department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    location: Clayton, VIC 3800
    email: emi.tanaka@monash.edu
  - name: Kate Hyde
    thanks: ""
    department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    location: Clayton, VIC 3800
    email: ""
  - name: Nicholas Tierney
    thanks: ""
    department: ""
    affiliation: ""
    location: ""
    email: ""
bibliography: ../references.bib
biblio-style: unsrt
#preamble: >
output: 
  bookdown::pdf_document2:
    template: TAS-template-for-rmd.tex
    keep_tex: true
date: "`r Sys.Date()`"
always_allow_html: true
---

```{r, child = "../paper.Rmd"}
```

>>>>

---
title: "The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth"
authors:
  - name: Dewi Amaliah
    thanks: "Test"
    department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    location: Clayton, VIC 3800
    email: dama0007@student.monash.edu
  - name: Dianne Cook
    department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    location: Clayton, VIC 3800
    email: dicook@monash.edu
  - name: Emi Tanaka
    department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    location: Clayton, VIC 3800
    email: emi.tanaka@monash.edu
  - name: Kate Hyde
    thanks: ""
    department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    location: Clayton, VIC 3800
    email: ""
  - name: Nicholas Tierney
    thanks: ""
    department: ""
    affiliation: ""
    location: ""
    email: ""
bibliography: ../references.bib
biblio-style: unsrt
#preamble: >
output: 
  bookdown::pdf_document2:
    template: TAS-template-for-rmd.tex
    keep_tex: true
date: "`r Sys.Date()`"
always_allow_html: true
---

```{r, child = "../paper.Rmd", eval = FALSE}
```
